Testing with Grein et al. data

### 2020-06-27 dev/hmm_grein.Rmd
Tweaks to m4

m4_rate_data <- rbind(
  tibble(.from = paste0(disease_levels, "_worsening"), .to = "Death", rate_group = "death"),
  tibble(.from = "AA_improving", .to = "Discharge", rate_group = "improve_one"),
  tibble(.from = paste0(disease_levels[2 : length(disease_levels)], "_improving"), 
             .to = paste0(disease_levels[1 : (length(disease_levels) - 1)],"_improving"), 
             rate_group = "improve_one"),
  tibble(.from = paste0(disease_levels[1 : (length(disease_levels) - 1)],"_worsening"), 
             .to = paste0(disease_levels[2 : length(disease_levels)], "_worsening"), 
             rate_group = "worsen_one"),
  tibble(.from = paste0(disease_levels,"_stable"), 
             .to = paste0(disease_levels, "_improving"), 
             rate_group = "to_improving"),
  tibble(.from = paste0(disease_levels,"_stable"), 
             .to = paste0(disease_levels, "_worsening"), 
             rate_group = "to_worsening"),
  tibble(.from = paste0(disease_levels,"_worsening"), 
             .to = paste0(disease_levels, "_stable"), 
             rate_group = "worsening_to_stable"),
  tibble(.from = paste0(disease_levels,"_improving"), 
             .to = paste0(disease_levels, "_stable"), 
             rate_group = "improving_to_stable")
  ) %>%
  mutate(.rate_id = factor(1:n())) %>%
  recode_group("death") %>%
  recode_group("improve_one") %>%
  recode_group("worsen_one") %>%
  recode_group("to_improving") %>%
  recode_group("to_worsening") %>%
  recode_group("improving_to_stable") %>%
  recode_group("worsening_to_stable")

@@

m4_formula <- update.formula(m2_formula,
  ~ . + is_improving_to_stable + is_worsening_to_stable + (0 + is_improving_to_stable | improving_to_stable_id) + 
    (0 + is_worsening_to_stable | worsening_to_stable_id))

@@

m4_fit <- brmhmm(m4, cache_file = paste0(cache_dir,"/grein_m4.rds"), control = list(adapt_delta = 0.9))

@@

>>>>

m4_rate_data <- rbind(
  tibble(.from = paste0(disease_levels, "_worsening"), .to = "Death", rate_group = "death"),
  tibble(.from = "AA_improving", .to = "Discharge", rate_group = "improve_one"),
  tibble(.from = paste0(disease_levels[2 : length(disease_levels)], "_improving"), 
             .to = paste0(disease_levels[1 : (length(disease_levels) - 1)],"_improving"), 
             rate_group = "improve_one"),
  tibble(.from = paste0(disease_levels[1 : (length(disease_levels) - 1)],"_worsening"), 
             .to = paste0(disease_levels[2 : length(disease_levels)], "_worsening"), 
             rate_group = "worsen_one"),
  tibble(.from = paste0(disease_levels,"_stable"), 
             .to = paste0(disease_levels, "_improving"), 
             rate_group = "to_improving"),
  tibble(.from = paste0(disease_levels,"_stable"), 
             .to = paste0(disease_levels, "_worsening"), 
             rate_group = "to_worsening"),
  tibble(.from = paste0(disease_levels,"_worsening"), 
             .to = paste0(disease_levels, "_stable"), 
             rate_group = "worsening_to_stable"),
  tibble(.from = paste0(disease_levels,"_improving"), 
             .to = paste0(disease_levels, "_stable"), 
             rate_group = "improving_to_stable"),
  tibble(.from = paste0(disease_levels,"_improving"), 
             .to = paste0(disease_levels, "_worsening"), 
             rate_group = "improving_to_worsening"),
  tibble(.from = paste0(disease_levels,"_worsening"), 
             .to = paste0(disease_levels, "_improving"), 
             rate_group = "worsening_to_improving")
  ) %>%
  mutate(.rate_id = factor(1:n())) %>%
  recode_group("death") %>%
  recode_group("improve_one") %>%
  recode_group("worsen_one") %>%
  recode_group("to_improving") %>%
  recode_group("to_worsening") %>%
  recode_group("improving_to_stable") %>%
  recode_group("worsening_to_stable") %>%
  recode_group("improving_to_worsening") %>%
  recode_group("worsening_to_improving")

@@

m4_formula <- update.formula(m2_formula,
  ~ . + is_improving_to_stable + is_worsening_to_stable + is_improving_to_worsening + is_worsening_to_improving +
    (0 + is_improving_to_stable | improving_to_stable_id) + 
    (0 + is_worsening_to_stable | worsening_to_stable_id) +
    (0 + is_improving_to_worsening | worsening_to_improving_id) + 
    (0 + is_worsening_to_improving | improving_to_worsening_id) 
  )

@@

m4_fit <- brmhmm(m4, cache_file = paste0(cache_dir,"/grein_m4.rds"), control = list(adapt_delta = 0.9), cores = 1)

@@

```{r}
# m4_hidden_state_data <- rbind(
#   tibble(base = disease_levels) %>% mutate(corresponding_obs = base) %>% 
#     crossing(tibble(state_group = c("_improving", "_stable", "_worsening"))) %>% 
#     mutate(id = factor(paste0(base, state_group))) %>%
#     select(-base, -state_group),
#   tibble(id = c("Death","Discharge")) %>% mutate(corresponding_obs = id)
# )
# 
# m4_observed_state_data <- m1_observed_state_data
# 
# m4_rate_data <- rbind(
#   tibble(.from = paste0(disease_levels, "_worsening"), .to = "Death", rate_group = "death"),
#   tibble(.from = "AA_improving", .to = "Discharge", rate_group = "improve_one"),
#   tibble(.from = paste0(disease_levels[2 : length(disease_levels)], "_improving"), 
#              .to = paste0(disease_levels[1 : (length(disease_levels) - 1)],"_improving"), 
#              rate_group = "improve_one"),
#   tibble(.from = paste0(disease_levels[1 : (length(disease_levels) - 1)],"_worsening"), 
#              .to = paste0(disease_levels[2 : length(disease_levels)], "_worsening"), 
#              rate_group = "worsen_one"),
#   tibble(.from = paste0(disease_levels,"_stable"), 
#              .to = paste0(disease_levels, "_improving"), 
#              rate_group = "to_improving"),
#   tibble(.from = paste0(disease_levels,"_stable"), 
#              .to = paste0(disease_levels, "_worsening"), 
#              rate_group = "to_worsening"),
#   tibble(.from = paste0(disease_levels,"_worsening"), 
#              .to = paste0(disease_levels, "_stable"), 
#              rate_group = "worsening_to_stable"),
#   tibble(.from = paste0(disease_levels,"_improving"), 
#              .to = paste0(disease_levels, "_stable"), 
#              rate_group = "improving_to_stable"),
#   tibble(.from = paste0(disease_levels,"_improving"), 
#              .to = paste0(disease_levels, "_worsening"), 
#              rate_group = "improving_to_worsening"),
#   tibble(.from = paste0(disease_levels,"_worsening"), 
#              .to = paste0(disease_levels, "_improving"), 
#              rate_group = "worsening_to_improving")
#   ) %>%
#   mutate(.rate_id = factor(1:n())) %>%
#   recode_group("death") %>%
#   recode_group("improve_one") %>%
#   recode_group("worsen_one") %>%
#   recode_group("to_improving") %>%
#   recode_group("to_worsening") %>%
#   recode_group("improving_to_stable") %>%
#   recode_group("worsening_to_stable")
#  
# 
# m4_initial_states <- series_data %>% filter(.time == 1) %>% arrange(.serie) %>% pull(.observed) %>% paste0(., "_worsening")
# 
# m4_prior = m1_prior
# 
# m4_formula <- update.formula(m2_formula,
#   ~ . + is_improving_to_stable + is_worsening_to_stable + (0 + is_improving_to_stable | improving_to_stable_id) + 
#     (0 + is_worsening_to_stable | worsening_to_stable_id))
#   
# m4 <- brmshmmdata(m4_formula, series_data, 
#                   m4_rate_data, m4_hidden_state_data, m4_initial_states, prior = m4_prior,
#                   observed_state_data = m1_observed_state_data)
# 
# m4_fit <- brmhmm(m4, cache_file = paste0(cache_dir,"/grein_m4.rds"), control = list(adapt_delta = 0.9))
# 
# summary(m4_fit$brmsfit)
```
